Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-16 papers/B1555_EdgeOn/B1555_letter.tex
update Table2 paras (SIE+expdisk only, zl=1.0)

We have created two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =$?? [{\bf WHAT VALUE DID
    WE USE??}].  The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$92.90$ &	$95.05$	  \\
$M_{tot} / \sigma_2$& $1.17\times 10^{10} $  &$81.36$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\hline
\end{tabular}

>>>>

We have created two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.  The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 lens model.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & \multicolumn{2}{c}{Lens model} \\
		&SIE+expdisk& 2-SIE		   
\\
\hline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$141.3$ &	$95.05$	  \\
$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$81.36$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\hline
\end{tabular}
